\textls[-0]{\thetitle}

### 2023-03-23 metatheory-condensed.tex
address comment

In rules \ruleref{l/add} and \ruleref{lsig/add},
the third premise $\goodTerm{\Gm,x : \TyTkg{\lsig}}{\seal}{A}$ is
responsible for hiding W-type signatures.
Here, $\TyTkg{\lsig}$ packages $\lsig$---recall that $\lsig$ contains the
(self-parameterized) types of all the fields preceding the current
field~$t$---into a dependent tuple type (\ruleref{tyeq/pk/add}).
The term $\seal$ turns a tuple of type $\TyTkg{\lsig}$ into a new tuple of type~$A$
that hides W-type signatures behind $\cU$, if necessary.\footnote{%
In the presence of hiding, it is important that the context type~$A$ be a
dependent tuple type rather than a linkage type; we expand on this issue in an
appendix.}
%
It is straightforward to find the~$\seal$ that fits the bill, though this process
is not automated in \TT.
In particular, when no hiding is needed, $\seal$ is simply~$x$,
%\EDJ{$\var{0}$ is not identity (substitution), but the first variable, right? Or you meant to say it is identity ``sealing''?}\YZreply{Yes, I meant identity sealing. I cannot say 'sealing' because the paper currently does not use the word sealing anywhere.}\EDJreply{What about just remove the parenthesis and ``the identity''}
and $A$ is $\TyTkg{\lsig}$.
In \cref{fig:stlc-linkage-typing}, $\seal_1$, $\seal_2$, and $\seal_{10}$ are simply $x$,
while $\seal_6$ hides $"tm" : \TyS{\wcode{\wsig_{\texttt{tm}}}}$
as $"tm" : \cU$ in $A_6$
so that the typing of~$t_6$ is oblivious to the concrete signature
$\wsig_{\texttt{tm}}$ and therefore can be reused.
%\begingroup
%\fontsize{9}{9}\selectfont%
%\goodTerm{
%  x :
%  \big[\texttt{tm} : \TyS{\wcode{\wsig_{\texttt{tm}}}},\ \texttt{tm\_unit} : \El{\texttt{tm}},\ \dadada\big]
%}{
%  \seal_6
%}{
%  \big[\texttt{tm} : \cU,\ \texttt{tm\_unit} : \El{\texttt{tm}},\ \dadada\big]
%}.
%\endgroup

>>>>

In rules \ruleref{l/add} and \ruleref{lsig/add},
the third premise $\goodTerm{\Gm,x : \TyTkg{\lsig}}{\seal}{A}$ is
responsible for hiding W-type signatures.
Here, $\TyTkg{\lsig}$ packages $\lsig$---recall that $\lsig$ contains the
(self-parameterized) types of all the fields preceding the current
field~$t$---into a dependent tuple type (\ruleref{tyeq/pk/add}).
The term $\seal$ turns a tuple of type $\TyTkg{\lsig}$ into a new tuple of type~$A$
that hides W-type signatures behind $\cU$, if necessary.\footnote{%
In the presence of hiding, it is important that the context type~$A$ be a
dependent tuple type rather than a linkage type; we expand on this point in an
appendix.}
%
It is straightforward to find the~$\seal$ that fits the bill, though this process
is not automated in \TT.
In particular, when no hiding is needed, $\seal$ is simply~$x$,
%\EDJ{$\var{0}$ is not identity (substitution), but the first variable, right? Or you meant to say it is identity ``sealing''?}\YZreply{Yes, I meant identity sealing. I cannot say 'sealing' because the paper currently does not use the word sealing anywhere.}\EDJreply{What about just remove the parenthesis and ``the identity''}
and $A$ is $\TyTkg{\lsig}$.
In \cref{fig:stlc-linkage-typing}, $\seal_1$, $\seal_2$, and $\seal_{10}$ are simply $x$,
while $\seal_6$ hides $"tm" : \TyS{\wcode{\wsig_{\texttt{tm}}}}$
as $"tm" : \cU$ in $A_6$
so that the typing of~$t_6$ is oblivious to the concrete signature
$\wsig_{\texttt{tm}}$ and therefore can be reused.
%\begingroup
%\fontsize{9}{9}\selectfont%
%\goodTerm{
%  x :
%  \big[\texttt{tm} : \TyS{\wcode{\wsig_{\texttt{tm}}}},\ \texttt{tm\_unit} : \El{\texttt{tm}},\ \dadada\big]
%}{
%  \seal_6
%}{
%  \big[\texttt{tm} : \cU,\ \texttt{tm\_unit} : \El{\texttt{tm}},\ \dadada\big]
%}.
%\endgroup

### 2023-03-23 metatheory2.tex
address comment

The problem lies in that the type $\TyLkg{\lsig^A}$ above cannot be inhabited.
Suppose there is some $\lkg^A$ such that $\cdot \vdash \lkg^A : \TyLkg{\lsig^A}$.
Then it follows from the self-parameterization that projecting out the field~$f$
has the typing
$\goodTerm{T_A : \cU, T_B: \cU}{\getfield{\lkg^A}{f}}{\El{T_A} \to \El{T_B}}$\EDJ{This field projection should be the usual one right? because ellA here is a linkage}.
This typing means that there is a function of type
$\nTyPi{T_A}{\cU}{\nTyPi{T_B}{\cU}{\El{T_A}
\to \El{T_B}}}$, i.e., a function from an arbitrary type to another arbitrary
type. We can easily derive inconsistency from this function:
we can apply it to $\top$ and $\bot$ and get $\top \to \bot$.

@@

Thus, it is critical that the hiding of W-type signatures operate on dependent
tuple types rather than linkage types.
In \TT, we introduce the syntax $\TyTkg{\lsig}$, $\Tkg{\lkg}$, and their computation rules to make
this hiding process more succinct.

>>>>

The problem lies in that the type $\TyLkg{\lsig^A}$ above cannot be inhabited.
Suppose there is some $\lkg^A$ such that $\cdot \vdash \lkg^A : \TyLkg{\lsig^A}$.
Then it follows from the self-parameterization that projecting out the last field~$f$
has the typing
$\goodTerm{T_A : \cU, T_B: \cU}{\lkgproj{2}{\lkg^A}}{\El{T_A} \to \El{T_B}}$.
This typing means that there is a function of type
$\nTyPi{T_A}{\cU}{\nTyPi{T_B}{\cU}{\El{T_A}
\to \El{T_B}}}$, i.e., a function from an arbitrary type to another arbitrary
type. We can easily derive inconsistency from this function:
we can apply it to $\top$ and $\bot$ and get $\top \to \bot$.

@@

Thus, it is critical that the hiding of W-type signatures operate on dependent
tuple types rather than linkage types.
To this end, we introduce the syntax $\TyTkg{\lsig}$ and its computation rules
(e.g., \ruleref{tyeq/pk/add}) to make it convenient to package linkage signatures
into dependent tuple types.
